Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-08-26 vesicle_code/docs/permeableVes/main.tex
working on stenosis runs

We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
with its long axis oriented in the $y$-direction. For all permeability
rates and shear rates, the semi-permeable vesicle tilts to an
inclination angle and undergoes tank treading behavior. However, because
of the semi-permeability, the initial and final reduced areas differ. In
Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
vesicle for various permeability rates, $\beta$, and shear rates
$\dot{\gamma}$. The shear rate has the largest effect on the final
reduced area.

\begin{figure}[htp]
  \centering
  %\ifTikz
  %\input{figures/shearPhaseDiagramRA2.tikz}
  %\fi
  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$.}
\end{figure}

@@

We next examine the effect of the non-linear Poiseuille flow on the
migration of semi-permeable vesicle. In this experiment, the vesicle is
initialized above the center line $y=0$. At sufficiently large reduced
areas and maximum velocities, the steady state vesicle configuration is
axisymmetric along the center line (parachute or bullet). In contrast,
for small reduced areas and maximum velocities, the steady-state shape
is axisymmetric, above the center line, and undergoes a tank treading
motion (slipper). These dynamics are investigated by Danker et
al.~\cite{dan-vla-mis2009} and Kaoui et al.~\cite{kao-bir-mis2009}. To
validate our methods, in Figure~\ref{fig:parabolicOffCenterPhaseDiagram}
we reconstruct the phase diagram for an impermeable
vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
qualitatively agree, Kaoui et al.~report that the vesicles with
$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
axisymmetric. In our simulations these vesicles are slightly asymmetric,
are undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

\begin{figure}[htp]
  \ifTikz
  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
  \fi
  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
  an impermeable vesicle with several different flow rates $U$ and
  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
  the final vesicle shape is either an axisymmetric parachute or bullet
  (pink region) or an asymmetric slipper (yellow region).}
\end{figure}

\begin{figure}[htp]
  \ifTikz
  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
  \fi
%  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
%  an impermeable vesicle with several different flow rates $U$ and
%  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
%  the final vesicle shape is either an axisymmetric parachute or bullet
%  (pink region) or an asymmetric slipper (yellow region).}
\end{figure}

>>>>

We initialize an elliptical vesicle with reduced area $\nu = 0.65$, and
with its long axis oriented in the $y$-direction. For all permeability
rates and shear rates, the semi-permeable vesicle tilts to an
inclination angle and undergoes tank treading dynamics. Because of the
semi-permeability, the initial and final reduced areas differ. In
Figure~\ref{fig:shearPhaseDiagram}, we plot the final shape of the
vesicle for various permeability rates, $\beta$, and shear rates
$\dot{\gamma}$. The shear rate has the largest effect on the final
reduced area.

\begin{figure}[htp]
  \centering
  %\ifTikz
%  \input{figures/shearPhaseDiagramRA2.tikz}
  %\fi
  \includegraphics[width=\linewidth]{figures/shearPhaseDiagramRA2.pdf}
  \caption{\label{fig:shearPhaseDiagram} The steady state shape of a
  semi-permeable vesicle with several different permeability rates
  $\beta$ and shear rates $\dot{\gamma}$. The final reduced areas are
  reported for the largest and smallest parameter values. The final
  reduced area decreases with the flow rate, while the permeability rate
  has a very small effect on the steady state shape.}
\end{figure}

@@

We next examine the effect of the non-linear Poiseuille flow on the
migration of semi-permeable vesicle. In this experiment, the vesicle is
initialized above the center line $y=0$. At sufficiently large reduced
areas and maximum velocities, the steady state vesicle configuration is
axisymmetric along the center line (parachute or bullet). In contrast,
for small reduced areas and maximum velocities, the steady-state shape
is axisymmetric, above the center line, and undergoes a tank treading
motion (slipper). These dynamics are investigated by Danker et
al.~\cite{dan-vla-mis2009} and Kaoui et al.~\cite{kao-bir-mis2009}. To
validate our methods, in
Figure~\ref{fig:parabolicOffCenterImpermeablePhaseDiagram} we
reconstruct the phase diagram for an impermeable
vesicle~\cite{kao-bir-mis2009} (see Figure 2). While the vesicle shapes
qualitatively agree, Kaoui et al.~report that the vesicles with
$\nu=0.7$ and flow rates $U = 1200 \mu m/s$ and $U = 1600 \mu m/s$ are
axisymmetric. In our simulations these vesicles are slightly asymmetric,
are undergoing a tank treading motion, and we therefore report them as
asymmetric slippers.

\begin{figure}[htp]
  \ifTikz
  \input{figures/parabolicOffCenterPhaseImpermeable.tikz}
  \fi
  \caption{\label{fig:parabolicOffCenterImpermeablePhaseDiagram} Phase
  diagram of an impermeable vesicle with several different flow rates
  $U$ and reduced areas $\nu$. As shown by Kaoui et
  al.~\cite{kao-bir-mis2009}, the final vesicle shape is either an
  axisymmetric parachute or bullet (pink region) or an asymmetric
  slipper (yellow region).}
\end{figure}

\begin{figure}[htp]
  \ifTikz
  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
  \fi
  \caption{\label{fig:parabolicOffCenterSemipermeablePhaseDiagram} Phase
  diagram of an semi-permeable vesicle, with $\beta = 10^{-3}$, with
  several different flow rates $U$ and reduced areas $\nu$. The
  steady-state reduced area for each flow rate, which is reported along
  the top of the vesicles, is nearly independent of the initial reduced
  area. Low flow rates result in axisymmetric vesicles with large
  reduced area, and high flow rates result in asymmetric vesicles with
  low reduced area. Results at higher flow rates are not eporeted since
  the vesicle self-intersects.}
\end{figure}
